\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-13 paper.tex
finished section algebraic data types

>>>>

    \section{A Case Study}

    In order to properly illustrate the monadic techniques described on section 5, a case study will be conducted on creating a parser in a monadic way for a simple programming language with the following constructs:

    \begin{itemize}
        \item Only \textit{Integer} and \textit{String} variable declarations \\
        \textbf{Integer} a = 42 or \textbf{String} b = `Hello Monads!'
        \item Output functions \\ 
        \textbf{print}(a)
        \item Input functions \\
        \textbf{get}(a)
        \item Variables assignments and operators \\ 
        a \textbf{:=} b where a and b are variables \\ 
        a \textbf{:=} b op c where a, b, and c are variables and op is an \textit{arithmetic operator} (*, /, +, -) or a \textit{comparison operator} (==, !=, $<$=, $<$, $>$=, $>$) 
        \item While loop \\ 
        \textbf{while}(\textit{condition}) \textbf{do} \textit{statements} \textbf{od}
    \end{itemize}

    \subsection{Algebraic Data Types}

    In order to parse any of the statements of this simple programming language, an algebraic data type type namely \textbf{AST} needs to be created. This \textbf{AST} will provide a tree representation of the abstract structure of the programming language. The \textit{Abstract Syntax Tree} is illustrated below:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
        data AST = DeclarationInt String Int 
                 | DeclarationString String String
                 | Print String
                 | Get String
                 | AssignmentVar String String
                 | AssignmentOp String String Operator String 
                 | WhileLoop Condition [AST] deriving (Show)
    \end{lstlisting}
    \end{tcolorbox}

    \noindent Additionally the definition of the \textbf{Operator} and \textbf{Condition} data types has been defined:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    data Operator  = Multi | Div | Plus | Minus
                   | Equal | NotEqual
                   | GreaterThan | GreaterThanOrEqual 
                   | LessThan | LessThanOrEqual deriving (Show)

    data Condition = Condition String Operator String deriving (Show) 
    \end{lstlisting}
    \end{tcolorbox}
